More on the Slavnov products of spin chains, KP hierarchy tau and Baker-Akhiezer functions

### 2025-05-23 draft.tex
finish section on the ba function

Let us also define the product 
\begin{equation}
  g(z, \bm{v}) = \prod_{v_i\in \bm{v}} g(z; v_i)\; . 
\end{equation}
Now, it is easy to see that each Bethe root \( v_i \in \bm{v}\) is a
pole of \(g(z;\bm{v})\). Therefore, if \(\Gamma\) is a contour
containing all the Bethe roots \(\{v_j\}_{j=1}^n\), we have
\begin{equation}
  \frac{1}{2 \pi i}\oint_{\Gamma} \mathrm{d}z g(z; \bm{v}) = \sum_{j=1}^n
  \prod_{v_i \in \bm{v}\setminus \{v_j\}} g(z, v_i)\; .
\end{equation}
Putting all these facts together, the coefficients \(L_{jk}\) are given by
\begin{equation}
  L_{jk} = g(u_k, \bm{u}_k) \mathcal{Y}(u_k; \bm{u}_j)\; ,
\end{equation}
and from this expression one can calculate the matrix \(\bm{M}\).

@@

\begin{proposition}
It has been established that tau functions in the alternant
form~(\ref{eq:slav-tau-function}) admits the following integral
representation
\begin{subequations}
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \right)\; ,
\end{equation}
where 
\begin{equation}
  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p} \quad \Leftrightarrow \quad
  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; . 
\end{equation}
In the above integral, we consider that integration curve \(\gamma_k\)
encloses all poles except the Bethe root \(v_k\).
\end{subequations}
\end{proposition}

@@

As far as we know, this result was first established
in~\cite{ZinnJustin:2002cr, ZinnJustin:2002pk}; see
also~\cite{Zinnjustin2009, Araujo:2021ghu} for further
discussions. Here, we present a proof of this result for pedagogical
reasons and to address some differences that arise due to our
conventions.
\todo{21/05}

In terms of the \(z\)-coordinates, the tau functions becomes
\begin{equation}
  \label{eq:tau-function}
  \bm{\tau}(\bm{z}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i}
    \prod_{l=1}^n \frac{1}{w - z_l} \frac{w^{n-j}\mathcal{Y}_k(w)}{w - v_k} \right) \; . 
\end{equation}
Now, it is easy to see that \(w =0\) is not a pole.  All in all, the
integration curve \(\gamma_k\) encloses points \(\{z_j\}_{j=1}^n\).

Let us define the invertible matrix \(\bm{\mathcal{K}}^T\) by its components
\begin{equation}
    \mathcal{K}_{kj} = 
\oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{z}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k}\;. 
\end{equation}
Explicitly, we have 
\begin{equation}
  \begin{split}
    \mathcal{K}_{kj}
    = & \oint_{\gamma_k} \frac{d w}{2\pi i} \frac{w^{n-j}}{\prod_{s} (w - z_s)}
    \frac{\mathcal{Y}_k(w)}{w - v_k} = \sum_{\ell =1}^n \frac{z_l^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)}
    \frac{\mathcal{Y}_k(z_\ell)}{z_\ell - v_k}\\
    & = \sum_{\ell = 1}^n  \Omega_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
  \end{split}
\end{equation}
where in the second line we have used the \(\bm{\Omega}\)-matrix
defined in~(\ref{eq:omega-matrix}).

It is easy to see that
\begin{equation}
  \begin{split}
  \det \bm{\mathcal{K}} & = \det(\bm{\Omega}) \det_{l,j}\left( \frac{z_l^{n-j}}{\prod_{j\neq l} (z_l - z_j)}\right) \\
  & = \det(\bm{\Omega}) \det_{l, j}(z_l^{n-j}) \prod_{\substack{j, l =1 \\ j \neq l}}^n (z_l - z_j)^{-1} \; .
  \end{split}
\end{equation}
We also have the identities 
\begin{subequations}
  \begin{equation}
	\det_{l,j}(z_l^{n-j}) = (-1)^{n(n-1)/2} \Delta(\bm{z})\; ,
  \end{equation}
  and
  \begin{equation}
	\prod_{\substack{j, l = 1 \\ j \neq l}}^n (z_l - z_j) = (-1)^{n(n-1)/2} \Delta(\bm{z})^2\; . 
  \end{equation}
\end{subequations}
Putting all these facts together, we finally see that 
\(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\), that
is preciselly the expression~(\ref{eq:slav-tau-function}).\\
\qed

One of the advantages of this representation is
that now it is easier to consider the limit of the infinite chain,
\(n\to \infty\).

@@

The Baker-Akhiezer (BA) funcion is defined in terms of the Japanese formula~\cite{Zabrodin2018}
\begin{equation}
  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
  \frac{\bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})}{\bm{\tau}(\bm{t}, \bm{v})}
\end{equation}
where 
\begin{equation}
  \bm{t} - [\lambda^{-1}] = 
  \{t_1 - \lambda^{-1}, t_2 - \lambda^{-2}/ 2 ,  t_2 - \lambda^{-3}/3, \dots,  t_p - \lambda^{-p}/p, \dots \}\; .
\end{equation}

Using the expression~(\ref{eq:tau-function-miwa}), we can write the
Baker-Akhiezer function in terms of the \(z\)-coordinates.
Let us first write
\begin{equation}
  t_p - \lambda^{-p}/p = \frac{1}{p} \sum_{j=1}^n z_j^ p - \lambda^{-p}/p \; , 
\end{equation}
therefore
\begin{equation}
  \begin{split}
    e^{\xi(\bm{t} - [\lambda^{-1}], w^{-1})} & = \exp\left[ \sum_{p=1}^\infty \left(t_p  - \frac{\lambda^{-p}}{p}\right) w^{-p} \right]\\
    & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ - \sum_{p=1}^\infty \frac{\lambda^{-p}}{p} w^{-p} \right] \\
    & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ \ln ( 1 - 1 / (\lambda w)) \right]
      = \left( 1 - \frac{1}{\lambda w}\right)  \prod_{j=1}^n \frac{1}{1 -  z_j /w} \\
    & = \frac{w^{n-1}}{\lambda } \left( \lambda w - 1 \right)  \prod_{j=1}^n \frac{1}{w -  z_j} \\
  \end{split}
\end{equation}

Using these expressions, we can write 
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
  \det_{j,k}\left[
  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{- j -1} ( \lambda w - 1) \mathcal{Y}_k(w)}{\lambda(w - v_k)} 
  \right]\; .
\end{equation}
that in terms of the \(z\)-coordinates becomes
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})
  & = \det_{j,k}\left[\oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}  
    \frac{( \lambda w - 1) w^{n-j-1}\mathcal{Y}_k(w)}{\lambda(w - v_k)} \right]\\
  & = \det_{j,k}\left[
    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}  
    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
    \right]
\end{split}
\end{equation}
where we have defined the function 
\begin{equation}
  \widehat{\mathcal{Y}}_k(w; \lambda)
  = \frac{( \lambda w - 1)}{\lambda} \mathcal{Y}_k(w) \; ,
\end{equation}
From these expressions, it is easy to see that for \(j=n\) the point
\(w = 0\) is a pole; and we must consider it in the integration curve \(\gamma_k\).

It is convenient to define the components
\begin{equation}
  \begin{split}
    \widetilde{\mathcal{K}}_{kj} = &
    \oint_{\tilde \gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
    + \delta_{nj} F_k(\lambda) \\
    & = \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
    + F_k(\lambda)\delta_{nj}  \\
  \end{split}
\end{equation}
where \(\tilde{\gamma}_k\) is a deformation contour that does not pick
the point \(w=0\); and
\begin{equation}
  \widehat{\Omega}_{k\ell}
  = \frac{1}{z_\ell} \frac{\widetilde{\mathcal{Y}}_k(\lambda, z_\ell)}{z_\ell - v_k}
  = \frac{(\lambda z_\ell -1)}{\lambda z_\ell} {\Omega}_{k\ell} 
\; , \qquad 
 F_k(\lambda) = (-1)^{n+1} \frac{\widehat{\mathcal{Y}}_k(0; \lambda)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
\end{equation}

In order to simplify our analysis, let us define one more matrix
\(\widehat{\mathcal{K}}\) by its components
\begin{equation}
    \widehat{\mathcal{K}}_{kj} = 
    \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell}
    \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
    \; .
\end{equation}
We conclude that \(\widetilde{\mathcal{K}}\) can be obtained from 
\(\widehat{\mathcal{K}}\) by adding to each component of the \(n\)-th row
the corresponding component of the vector \(\bm{F} = (F_1, \dots , F_n)\). 
Let us write this operation as 
\begin{equation}
  \widetilde{\mathcal{K}} = \widehat{\mathcal{K}} + \bm{0}_{[ \bm{F} \to n-row]}\; . 
\end{equation}
Where we use the notation \(\mathcal{A}_{[ \bm{F} \to j-row]} \) to
denote the replacement of the \(j-th\) row of the matrix with the
vector \(\bm{F}\).  Above we have considered this operation with the
zero matrix \(\bm{0}\).

By the multilinearity of the determinant, we can write
\begin{equation}
  \det \widetilde{\mathcal{K}} = 
    \det \widehat{\mathcal{K}} + 
    \det \widehat{\mathcal{K}}_{[\bm{F} \to n-row]}\; .
\end{equation}

It is now easy to see that \(\det \widehat{\mathcal{K}}\) is
proportional to the tau functions (Slavnov products), that is
\begin{equation}
    \det \widehat{\mathcal{K}}  = 
    \det(\widehat{\Omega})
    \det_{l,j}
    \left( \frac{z_l^{n-j}}{\prod_{s\neq l} (z_l - z_s)} \right)\\
    = \frac{\det(\widehat{\Omega})}{\Delta(\bm{z})}
\end{equation}
where \(\widehat{\Omega}\) is the matrix formed by the components
\(\widehat{\Omega}_{i,j}\). The above determinant is itself a tau function,
but we can also write is as
\begin{equation}
    \det \widehat{\mathcal{K}} = 
    \frac{\det(\Omega)}{\Delta(\bm{z})}
    \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) 
    = \bm{\tau}(\bm{z}, \bm{v}) \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) \; . 
\end{equation}

Finally, using the elementary symmetric polynomials \(\sigma_p^{(n)}\), we write
\begin{equation}
  \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) = 1 + 
  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})\; , 
\end{equation}
where \( \bm{z}^{-1} = \{z_1^{-1}, z_2^{-1}, \dots , z_n^{-1}\}\).

Putting all these facts together, we write the Baker-Akhiezer function
as 
\begin{equation}
  \psi(\lambda; \bm{z}, \bm{v}) =
  e^{\xi(\bm{t}, \lambda)}  \left[ 1 + 
  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})
    + \frac{1}{\bm{\tau}(\bm{z}, \bm{v})}
    \det \widehat{\mathcal{K}}_{[\bm{F} \to n-row]}
  \right]\; .
\end{equation}
Next section we find a better expression for the Baker-Akhiezer
function, but from this expression we can see that all the poles
are at the point \(\lambda =0\).

%%% Maybe I should calculate some examples
%\subsection{Examples} Let us now consider the cases \(n=2, 3\).
%We have calculated the tau functions for these objets. The
%elementary symmetric polynomials are also known. Therefore,
%the only detail we need to complete now is the calculation of
%the matrix \(\widehat{\mathcal{K}}\). 
%
%\subsubsection{n=2} We
%we have \(\mathcal{Y}_j\) for \(j=1,2\) and two Bethe roots

@@

We now want to consider the above calculations in the Miwa
coordinates.

We define the matrix \(\check{\mathcal{K}}(\lambda)\) by its components
\begin{equation}
    \check{\mathcal{K}}_{jk} = -
    \oint_{\gamma_k} \frac{dw}{2\pi i}
    e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; .
\end{equation}

Therefore, we have that 
\begin{equation}
  \widetilde{\mathcal{K}}_{kj} = 
  \mathcal{K}_{kj}  + \frac{1}{\lambda}
  \check{\mathcal{K}}_{kj}
  \ \Leftrightarrow \
  \widetilde{\mathcal{K}} = 
  \mathcal{K} + \frac{1}{\lambda}
  \check{\mathcal{K}}\; , 
\end{equation}
and since \(\mathcal{K}\) is invertible, we get
\begin{equation}
  \widetilde{\mathcal{K}} = 
  \mathcal{K}\left( \mathbb{1} + 
  \frac{1}{\lambda}\mathcal{K}^{-1}\check{\mathcal{K}} \right)\; .
\end{equation}

Putting all these facts together, we find that the shifted
tau-functions are
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
  \bm{\tau}(\bm{t}, \bm{v})
  \det \left( \mathbb{1} + \frac{1}{\lambda}
  \mathcal{K}^{-1} \check{\mathcal{K}} \right)\; .
\end{equation}

>>>>

Let us also define the product 
\begin{equation}
  g(z, \bm{v}) = \prod_{v_i\in \bm{v}} g(z; v_i)\; . 
\end{equation}
Now, it is easy to see that each Bethe root \( v_i \in \bm{v}\) is a
pole of \(g(z;\bm{v})\). Therefore, if \(\Gamma\) is a contour
containing all the Bethe roots \(\{v_j\}_{j=1}^n\), we have
\begin{equation}
  \frac{1}{2 \pi i}\oint_{\Gamma} \mathrm{d}z g(z; \bm{v}) = \sum_{j=1}^n
  \prod_{v_i \in \bm{v}\setminus \{v_j\}} g(z, v_i)\; .
\end{equation}
Consequently, the coefficients \(L_{jk}\) are given by
\begin{equation}
  L_{jk} = g(u_k, \bm{u}_k) \mathcal{Y}(u_k; \bm{u}_j)\; ,
\end{equation}
and from this expression one can calculate the matrix \(\bm{M}\).

@@

\begin{proposition}
\label{prop:integral-rep}
It has been established that tau functions in the alternant
form~(\ref{eq:slav-tau-function}) admits the following integral
representation
\begin{subequations}
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \right)\; ,
\end{equation}
where 
\begin{equation}
  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p} \quad \Leftrightarrow \quad
  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; . 
\end{equation}
In the above integral, we consider that integration curve \(\gamma_k\)
encloses all poles except the Bethe root \(v_k\).
\end{subequations}
\end{proposition}

@@

As far as we know, this result was first established
in~\cite{ZinnJustin:2002cr, ZinnJustin:2002pk}; see
also~\cite{Zinnjustin2009, Araujo:2021ghu} for further
discussions. Here, we present a proof of this result for pedagogical
reasons and to address some differences that arise due to our
conventions.

In terms of the \(z\)-coordinates, the integral~(\ref{eq:tau-function-miwa}) becomes
\begin{equation}
  \label{eq:tau-function}
  \bm{\tau}(\bm{z}, \bm{v}) =
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i}
    \prod_{l=1}^n \frac{1}{w - z_l} \frac{w^{n-j}\mathcal{Y}_k(w)}{w - v_k} \right) \; . 
\end{equation}
Since \(n \geq j\), the point \(w = 0\) is not a pole of the
integrand. All in all, the integration contour \(\gamma_k\) encloses
the points \(\{z_j\}_{j=1}^n\).

Let us define the matrix\footnote{
The choice of the transposition is an aesthetic one. We want 
to derive a result expressed as a matrix product with the components \(\Omega_{kl}\) on the left.}
\(\bm{\mathcal{K}}^T\) by its components as follows:
\begin{equation}
\label{eq:k-matrix}
    \mathcal{K}_{kj} = 
\oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{z}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k}\; .
\end{equation}
We can now carry out the integration
\begin{equation}
  \begin{split}
    \mathcal{K}_{kj}
    = & \oint_{\gamma_k} \frac{d w}{2\pi i} \frac{w^{n-j}}{\prod_{s} (w - z_s)}
    \frac{\mathcal{Y}_k(w)}{w - v_k} = \sum_{\ell =1}^n \frac{z_l^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)}
    \frac{\mathcal{Y}_k(z_\ell)}{z_\ell - v_k}\\
    & = \sum_{\ell = 1}^n  \Omega_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)\; ,
  \end{split}
\end{equation}
where in the second line we have used the \(\bm{\Omega}\)-matrix
defined in~(\ref{eq:omega-matrix}).

We can now see that the matrix \(\bm{\mathcal{K}}\) can be understood
as the product of two other matrices. Consequently, we have
\begin{equation}
  \begin{split}
  \det \bm{\mathcal{K}} & = \det(\bm{\Omega}) \det_{l,j}\left( \frac{z_l^{n-j}}{\prod_{j\neq l} (z_l - z_j)}\right) \\
  & = \det(\bm{\Omega}) \det_{l, j}(z_l^{n-j}) \prod_{\substack{j, l =1 \\ j \neq l}}^n (z_l - z_j)^{-1} \; .
  \end{split}
\end{equation}
We also have the identities 
\begin{subequations}
  \begin{equation}
	\det_{l,j}(z_l^{n-j}) = (-1)^{n(n-1)/2} \Delta(\bm{z})\; ,
  \end{equation}
  and
  \begin{equation}
	\prod_{\substack{j, l = 1 \\ j \neq l}}^n (z_l - z_j) = (-1)^{n(n-1)/2} \Delta(\bm{z})^2\; . 
  \end{equation}
\end{subequations}
Combining all these expressions, we finally see that
\begin{equation}
  \det \bm{\mathcal{K}} = \frac{\det \bm{\Omega}}{\Delta(\bm{z})}\; ,
\end{equation}
then \(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\), that is
preciselly the expression~(\ref{eq:slav-tau-function}) for a fixed
\(\ell\). \\ \qed

\begin{lemma}
\label{lemma:k-invert}
The matrix \(\bm{\mathcal{K}}\) defined via~(\ref{eq:k-matrix}) is
invertible. This follows immediately from the relation
\(\bm{\tau}(\bm{z}, \bm{v}) = \det \bm{\mathcal{K}}\).
\end{lemma}

One advantage of the integral
representation~(\ref{eq:tau-function-miwa}) is that it makes it easier
to consider the limit of the infinite chain, \(n\to \infty\).

@@

The Baker-Akhiezer (BA) function is defined through the
Japanese formula~\cite{Babelon:2003qtg, Harnad:2021tau, Zabrodin2018}.
\begin{equation}
\label{eq:ba-function}
  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
  \frac{\bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})}{\bm{\tau}(\bm{t}, \bm{v})}\; ,
\end{equation}
where 
\begin{equation}
  \bm{t} - [\lambda^{-1}] = 
  \{t_1 - \lambda^{-1}, t_2 - \lambda^{-2}/ 2 ,  t_2 - \lambda^{-3}/3, \dots,  t_p - \lambda^{-p}/p, \dots \}\; .
\end{equation}
We can write these components as
\begin{equation}
  t_p - \frac{\lambda^{-p}}{p} = \frac{1}{p} \sum_{j=1}^n z_j^ p - \frac{\lambda^{-p}}{p} \; , 
\end{equation}
therefore
\begin{equation}
  \begin{split}
    e^{\xi(\bm{t} - [\lambda^{-1}], w^{-1})} & = \exp\left[ \sum_{p=1}^\infty \left(t_p  - \frac{\lambda^{-p}}{p}\right) w^{-p} \right]\\
    & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ - \sum_{p=1}^\infty \frac{\lambda^{-p}}{p} w^{-p} \right] \\
    & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ \ln ( 1 - 1 / (\lambda w)) \right]
      = \left( 1 - \frac{1}{\lambda w}\right)  \prod_{j=1}^n \frac{1}{1 -  z_j /w} \\
    & = \frac{w^{n-1}}{\lambda } \left( \lambda w - 1 \right)  \prod_{j=1}^n \frac{1}{w -  z_j} \; .
  \end{split}
\end{equation}

Finally, we express the shifted tau functions
\begin{subequations}
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
  \det_{j,k}\left[
  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{- j -1} ( \lambda w - 1) \mathcal{Y}_k(w)}{\lambda(w - v_k)} 
  \right]
\end{equation}
in terms of the \(z\)-coordinates as
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v}; \lambda^{-1})
  & = \det_{j,k}\left[\oint_{\gamma_k} \frac{dw}{2\pi i} 
    \frac{( \lambda w - 1) w^{n-j-1}\mathcal{Y}_k(w)}{\lambda(w - v_k)} \prod_{s=1}^n \frac{1}{w - z_s} \right]\\
  & = \det_{j,k}\left[
    \oint_{\gamma_k} \frac{dw}{2\pi i}  
    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)} \prod_{s=1}^n \frac{1}{w - z_s} 
    \right]\; ,
\end{split}
\end{equation}
\end{subequations}
where we have defined the functions
\begin{equation}
  \widehat{\mathcal{Y}}_k(w; \lambda)
  = \frac{( \lambda w - 1)}{\lambda} \mathcal{Y}_k(w) \; , \qquad k =1, \dots, n\;. 
\end{equation}
From these expressions, it is easy to see that for \(j = n\), the
point \(w = 0\) is a pole, and we must include it in the integration
contour \(\gamma_k\).

Define the matrix \(\widetilde{\bm{\mathcal{K}}}^T\) by its components
\begin{equation}
\label{eq:k-tilde}
  \begin{split}
    \widetilde{\mathcal{K}}_{kj} = &
\oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{- j -1} ( \lambda w - 1) \mathcal{Y}_k(w)}{\lambda(w - v_k)}
    \\
    = & \oint_{\gamma_k} \frac{dw}{2\pi i}  
    \frac{( \lambda w - 1) w^{n-j-1}\mathcal{Y}_k(w)}{\lambda(w - v_k)} \prod_{s=1}^n \frac{1}{w - z_s}  \\
    = &
    \oint_{\tilde \gamma_k} \frac{dw}{2\pi i}
    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)} \prod_{s=1}^n \frac{1}{w - z_s} 
    + \delta_{nj} F_k(\lambda) \\
    = & \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
    + F_k(\lambda)\delta_{nj}  \\
  \end{split}
\end{equation}
where \(\tilde{\gamma}_k\) is a deformed contour that does not enclose
the point \(w = 0\), and
\begin{equation}
\label{eq:omehat-comp}
  \widehat{\Omega}_{k\ell}
  = \frac{1}{z_\ell} \frac{\widehat{\mathcal{Y}}_k(z_\ell, \lambda)}{z_\ell - v_k}
  = \frac{(\lambda z_\ell -1)}{\lambda z_\ell} {\Omega}_{k\ell} 
\; , \qquad 
 F_k(\lambda) = (-1)^{n+1} \frac{\widehat{\mathcal{Y}}_k(0; \lambda)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
\end{equation}
Moreover, it is also convenient to define the matrix
\(\widehat{\bm{\Omega}}\) formed by the components
\(\widehat{\Omega}_{ij}\) and
the vector \(\bm{F} = (F_1, \dots , F_n)\), 
with the components defined above in~(\ref{eq:omehat-comp}).

Additionally, let us define yet another matrix,
\(\widehat{\bm{\mathcal{K}}}^T\), by
\begin{equation}
    \widehat{\mathcal{K}}_{kj} = 
    \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell}
    \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right) \; .
\end{equation}

We conclude that \(\widetilde{\bm{\mathcal{K}}}\) can be derived from
\(\widehat{\bm{\mathcal{K}}}\) by adding, component-wise, the vector
\(\bm{F} = (F_1, \dots , F_n)\) to the \(n\)-th row.  We write this
operation as
\begin{equation}
  \widetilde{\bm{\mathcal{K}}} = \widehat{\bm{\mathcal{K}}} + \bm{0}_{[ \bm{F} \to n\text{-row}]}\; . 
\end{equation}
Here we use the notation \(\mathcal{\bm{A}}_{[ \bm{F} \to j\text{-row}]}\) 
to denote the replacement of the \(j\)-th row of the matrix 
\(\mathcal{\bm{A}}\) with the vector \(\bm{F}\). In the expression above, 
we have considered this operation with the null matrix \(\bm{0}\).
By the multilinearity of the determinant, we finally have
\begin{equation}
  \det \widetilde{\bm{\mathcal{K}}} = 
    \det \widehat{\bm{\mathcal{K}}} + 
    \det \widehat{\bm{\mathcal{K}}}_{[\bm{F} \to n\text{-row}]}\; .
\end{equation}

It is now easy to see that \(\det \widehat{\bm{\mathcal{K}}}\) is
proportional to the Slavnov product, that is,
\begin{equation}
    \det \widehat{\bm{\mathcal{K}}}  = 
    \det(\widehat{\bm{\Omega}})
    \det_{l,j}
    \left( \frac{z_l^{n-j}}{\prod_{s\neq l} (z_l - z_s)} \right)\\
    = \frac{\det(\widehat{\bm{\Omega}})}{\Delta(\bm{z})}\;. 
\end{equation}
The above determinant is itself a tau function, but we can also write
it as
\begin{equation}
    \det \widehat{\mathcal{K}} = 
    \frac{\det(\Omega)}{\Delta(\bm{z})}
    \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) 
    = \bm{\tau}(\bm{z}, \bm{v}) \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) \; . 
\end{equation}
Furthermore, we can simplify this expression using the elementary
symmetric polynomials \(\sigma_p^{(n)}\); that is,
\begin{equation}
  \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) = 1 + 
  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})\; , 
\end{equation}
where \( \bm{z}^{-1} = \{z_1^{-1}, z_2^{-1}, \dots , z_n^{-1}\}\).

Collecting all these facts, we finally write the Baker-Akhiezer
function as
\begin{equation}
  \psi(\lambda; \bm{z}, \bm{v}) =
  e^{\xi(\bm{t}, \lambda)}  \left[ 1 + 
  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})
    + \frac{1}{\bm{\tau}(\bm{z}, \bm{v})}
    \det \widehat{\bm{\mathcal{K}}}_{[\bm{F} \to n\text{-row}]}
  \right]\; .
\end{equation}
From this expression we can see that all the poles are located at the
point \(\lambda = 0\).

@@

In this section, we find a better expression for the Baker-Akhiezer
function. Our main goal now is to reconsider the above calculations
using the Miwa coordinates.

Let us begin our exploration with the definitions~(\ref{eq:k-matrix})
and~(\ref{eq:k-tilde}). Let us write
\begin{equation}
\label{eq:ktilde-split}
  \widetilde{\mathcal{K}}_{kj} = \mathcal{K}_{kj}
  - \frac{1}{\lambda} \oint_{\gamma_k} \frac{dw}{2\pi i}
    e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; .
\end{equation}
Therefore, let us define one more matrix,
\(\check{\bm{\mathcal{K}}}^T\), with components given by
\begin{equation}
  \check{\mathcal{K}}_{jk} =
  - \oint_{\gamma_k} \frac{dw}{2\pi i}
    e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; .
\end{equation}
Therefore,~(\ref{eq:ktilde-split}) becomes
\begin{equation}
  \widetilde{\mathcal{K}}_{kj} = 
  \mathcal{K}_{kj}  + \frac{1}{\lambda}
  \check{\mathcal{K}}_{kj} \; , 
\end{equation}
that yields
\begin{equation}
  \widetilde{\bm{\mathcal{K}}} = 
  \bm{\mathcal{K}} + \frac{1}{\lambda}
  \check{\bm{\mathcal{K}}}\; .
\end{equation}
Moreover, by Lemma~\ref{lemma:k-invert}, \(\bm{\mathcal{K}}\) is
invertible; therefore,
\begin{equation}
  \widetilde{\bm{\mathcal{K}}} = 
  \bm{\mathcal{K}}\left( \mathbb{1} + 
  \frac{1}{\lambda}\bm{\mathcal{K}}^{-1}\check{\bm{\mathcal{K}}} \right)\; .
\end{equation}

Combining these results, we find that the shifted tau-functions are
\begin{equation}
  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
  \bm{\tau}(\bm{t}, \bm{v})
  \det \left( \mathbb{1} + \frac{1}{\lambda}
  \bm{\mathcal{K}}^{-1} \check{\bm{\mathcal{K}}} \right)\; .
\end{equation}
We finally conclude that the Bakher-Akhiezer
function~(\ref{eq:ba-function}) can be written as
\begin{equation}
\label{eq:ba-fredholm}
  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
  \det \left( \mathbb{1} + 
    \frac{1}{\lambda} \bm{\mathcal{M}}
  \right)\; , 
\end{equation}
where \(\bm{\mathcal{M}} =
\bm{\mathcal{K}}^{-1}\check{\bm{\mathcal{K}}}\) is a
finite-dimensional matrix depending on the coordinates
\(\bm{t}\).

Let us now use the elementary property
\begin{subequations}
\begin{equation}
  \begin{split}
    \det \left( \mathbb{1} + \frac{1}{\lambda} \bm{\mathcal{M}}\right)
    & = \exp \left[ \Tr \ln \left( \mathbb{1} + \frac{1}{\lambda} \bm{\mathcal{M}} \right) \right]
    = \exp\left[ \sum_{l=1}^n \ln \left( 1 + \frac{\mu_l}{\lambda} \right)\right]\\
    & = \prod_{l=1}^n \left( 1 + \frac{\mu_l}{\lambda} \right) \; ,
  \end{split}
\end{equation}
\end{subequations}
where \(\bm{\mu} = \{\mu_l\}_{l=1}^n\) are the eigenvalues of the
matrix \(\bm{\mathcal{M}}\), and these obviously depend on the Bethe
roots \(\bm{v}\) and parameters \(\bm{t}\).  Therefore, we have
\begin{equation}
  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
  \left(1 + \sum_{k=1}^n \frac{\xi_k(\bm{t})}{\lambda^k} 
  \right)\; \qquad \xi_k(\bm{t}) = \sigma_k^{(n)}(\bm{\mu})\; .
\end{equation}
